{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
continue to work on slides

\begin{frame}{LSN \textit{vs} Double null on TCV}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesLSN-DN}}
      \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58623}}
    \end{column}
    \begin{column}{0.5\textwidth}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{H-Mode effect of cryopumps}

@@

\begin{frame}{Program for 2018: AUG}
\end{frame}

\begin{frame}{Program for 2018: TCV}
\end{frame}

\begin{frame}{Program for 2018: MAST-U}
\end{frame}

>>>>

\begin{frame}{LSN \textit{vs} Double null on TCV}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesLSN-DN}}
      \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58623}}
      \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeLSN-DN}}
    \end{column}
    \begin{column}{0.5\textwidth}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{H-Mode effect of cryopumps}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot_34276_34278_InterELMprofiles}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}
    \end{column}
    \begin{column}{0.5\textwidth}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{Program for 2018: AUG}
  \begin{itemize}
     \item X-point manipulator (hopefully with NPH) triggered at
	the same time as MPM
     \item X-point vertical shift in order to have SP at different
	vertical heigth at the target
     \item DN discharges. With slow movement of the second X-point into the vessel
	to be performed at constant power/density where shoulder alreay exists
     \item USN with midplane/X-point manipulator to monitor the upstream SOL  \end{itemize}
\end{frame}

\begin{frame}{Program for 2018: TCV}
  \begin{itemize}
     \item H-Mode ?
      \item Long divertor legs (probe in the lower port)
      \item SnowFlake to monitor the fluctuations in between the 2 separatrix
	to be done in high density discharges
       \item Try to move the second X-point in SN divertor at a different
	Z position while keeping the same radial distances between the
	points
\end{itemize}
\end{frame}

\begin{frame}{Program for 2018: MAST-U}
  \begin{itemize}
     \item Influence of neutral recycling source in establishing upstream profiles
	and comparison between Low-RT and Vertical target. Look also ath the heat
	loads
      \item Current scan at constant q95/constant Bt
      \end{itemize}
\end{frame}
